\documentclass[12pt,a4paper]{article}

\usepackage{geometry}
\geometry{
    left=2cm, 
    right=2cm,
    top=3cm,  
    bottom=2cm
}

\usepackage[spanish,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\usepackage{graphicx}
\usepackage{wrapfig}

\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=ieee]{biblatex}
\addbibresource{docs.bib}

\usepackage{setspace}
\setstretch{1.5}

\begin{document}

\section*{SSS - DRD}
\begin{center} 
    \begin{tabular}{|c|l|c|l|}
        \hline
        \textbf{Información} & \multicolumn{3}{|c|}{Software System Specification} \\
        \hline
        \textbf{Proyecto:} & Book Explore & \textbf{Version:} & 12022025 \\    
        \hline
        \textbf{Preparado por:} & Alexis Aguilar & \textbf{Fecha:} & 12/Feb/2025 \\    
        \hline
        \textbf{Recibido por:} & Víctor de la Luz & \textbf{Status:} & En construcción \\    
        \hline
    \end{tabular}
\end{center}

\section{Introduction}
This document aims describing "Book Explorer" system based on exploring new 
titles using a story created by the user.

\section{Applicable and Reference Documents}
This document complies with the definitions contained in the 
ECSS-E-ST-40C standard dated March 6, 2009 \cite{ECSS-E-ST-40C}.

\section{Terms, Definitions and Abbreviated Terms}
\emph{UNAM}: Universidad Nacional Autónoma de México

\section{General Description}
\subsection{Product Perspective}
More than with other systems, its main relationship is with the 
Open Library API, from which most of the information in the books is obtained.
\subsection{General Capabilities}
The system will be able to recommend a series of books to the user using a 
story that the user creates using text displayed on the interface when using 
the system.
\subsection{General Constraints}
None at present.
\subsection{Operational Environment}
Both the system and the user must be connected to the Internet. In general, 
the system makes use of two interfaces: one to interact with the user and 
the other to communicate with Open Library to obtain data from the books.
\subsection{Assumptions and Dependencies}
None at present.

\section{Specific requirements}
\subsection{Capabilities Requirements}
The system should be able to interact with the user so 
that they can capture the type of stories they would 
like to be read by using short text representative of 
events or occurrences in the story to create a synopsis of their "ideal book".\\
In addition, the system should provide a response in 
the shortest possible time along with the most 
appropriate recommendations.
\subsection{System Interface Requirements}
Two interfaces are required to obtain the data concerning 
the books: one with the Open Library API and the other with 
DeepSeek to generate synopses concerning the books. 
Subsequently, one is required for communication with the 
databases and the recommender system itself. And a last one 
for the interaction with the user, for the capture of the 
story to be created.
\subsection{Adaptation and Missionization Requirements}
The books obtained from Open Library are the only data 
that could be radically altered or modified if the database 
is completely removed. And adding new titles could also 
create a disruption if it is a title with a new genre not previously recorded.
\subsection{Computer Resource Requirements}
\subsubsection{Computer Hardware Resource Requirements}
Server capable of supporting Docker images and sufficient storage for databases.
\subsubsection{Computer Hardware Utilization Requirements}
Undefined at present.
\subsubsection{Computer Software Resource Requirements}
Python as the main programming language, together with 
Flask for the creation of web interfaces. Postgres (SQL) and 
(Vector NoSQL) will be used for database management.
\subsection{Security Requirements}
[Data protection]
\subsection{Safety Requirements}
Undefined at present
\subsection{Reliability and Availability Requirements}
\subsection{Quality Requirements}
\subsection{Design Requirements and Constraints}
\subsection{Software Operations Requirements}
\subsection{Software Maintenance Requirements}
\subsection{System and Software Observability Requirements}

\section{Verification, Validation and System Integration}
\subsection{Verification and Validation Process Requirements}
\subsection{Validation Approach}
\subsection{Validation Requirements}
\subsection{Verification Requirements}

\section{System Models}

\newpage
\printbibliography

\end{document}